TODO: A Survey of StarCraft AI Techniques

### 2013-02-14 survey.tex
Start II.B.5 task decomposition

\subsubsection{Task Decomposition}
TODO }

>>>>

\subsubsection{Task Decomposition}
Playing a  RTS game like Starcraft  can be decomposed  into three main
tasks: 
\begin{itemize}
\item Strategy:  corresponds to the  decision making process.  This is
  the  highest level of  abstraction for  the game  comprehension. RTS
  games   are   all   about   finding   an   efficient   strategy   or
  counter-strategy  against a  given opponent.  It concerns  the whole
  set of  units and buildings  one owns. If  we may allow  ourselves a
  military analogy, strategy is orders given by generals at the HQ. 
\item  Tactics: are  the implementation  of the  current  strategy. It
  implies  army and  building positioning,  movements, timing,  and so
  on.  Tactics concerns a  group of  units. They  are orders  given by
  officers on the battlefield.
\item  Reactive  control:  is  the  implementation  of  tactics.  This
  consists in   moving,    targeting,   firing,    fleeing   during
  battle. Reactive control focuses on  a specific unit. It is soldiers
  applying officers' orders.
\end{itemize}

\noindent
Both     strategy      and     tactics     are      usually     called
\textit{macro-management},  whereas reactive  control  is also  called
\textit{micro-management}. In addition of the three tasks shown above,
one could also consider these two tasks that an AI has to deal with:
\begin{itemize}
\item Terrain analysis: consists  in the analysis of regions composing
  the  map,  chokes,  minerals  and  gas emplacements,  low  and  high
  walkable grounds, islands, etc.
\item Intelligence gathering:  corresponds to information collected on
  our  opponent. Because of  the fog  of war,  a non-cheating  AI must
  regulary send scouts to localize and spy enemy bases, and must see or
  infer what buildings and technology the enemy has developed in order
  to adapt its strategy.
\end{itemize}

\noindent
The reader can find a good presentation of task decomposition for AIs 
playing RTS in~\cite{weber2011acs}.  }
